\section{Milestone chart (time schedule)}
\label{sect:milestones}
%TC:ignore
\todo[inline]{Give a detailed schedule of how the project will be carried out. What is the project timeline and when will particularly meaningful points, referred to as milestones, be completed? What is the deliverable for each of these milestones? For example:}
%TC:endignore
The project will start on 25 August and end at 00:00 on 30 August. There will be the following milestones and deliverables:

%TC:ignore
\begin{description}
\item{26 August} working multicast server and client

\item{27 August} prepare testbed and perform experimental runs for each of the
  different numbers of clients to be completed (as per above) and stored in
  two comma separated files (ACK.csv and NACK.csv) which each line consisting
  of: number of clients, number of packets. Data will be collected using a
  separate computer running Wireshark. Analysis of the data and development of
  the analytic model will proceed in parallel with the data collection.

\item{28 August} model completed based upon using the statistical package R to do the curve fitting to the experimental data

\item{29 August} evaluation of model for additional data points to be check by new experimental runs to check that the model accurately produces the expected number of packets for the given number of clients for both \gls{ACK} and \gls{NACK} alternatives.

\item{Before 30 August} submit final report (the report will have been written in parallel with each of the above steps)
\end{description}
%TC:endignore